Probing the internal structure of quasars using microlensing events

### 2016-03-09 paper1/fitting.tex
fixed one typo
reprocessed eps files

\begin{figure}
\centering
\includegraphics[width=0.9\hsize,bb=0 0 576 432
                ]{plots/data_cc.eps}
\includegraphics[width=0.9\hsize,bb=0 0 576 432
                ]{plots/data_dd.eps}
\includegraphics[width=0.9\hsize,bb=0 0 576 432
                ]{plots/data_gg.eps}
\caption{\label{fig:mockdata} Three different mock datasets with
  three different parametrizations fitted to each --- crescent (red),
  uniform-disk (blue) and Gaussian disk (green).}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize,bb=0 0 576 432
                  ]{plots/Rp4all.eps}
\caption{\label{fig:mcmc} Posterior probability distribution for the
  source size $R_p$.  The vertical line is the correct value. Same
  color represents the same dataset whereas same line style
  corresponds to same model fit.  The legend gives the reduced
  $\chi^2$ of the best fit in each case.}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize,bb=0 0 576 432
                  ]{plots/Rhalf_RnRp.eps}
  \includegraphics[width=0.9\hsize,bb=0 0 576 432
                  ]{plots/aRp_bRp.eps}
\caption{\label{fig:crescentfit} The 2$\sigma$ contours (or error ellipses)
  of the crescent model when fitting with the three different
  datasets.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\hsize,bb=0 0 576 432
                ]{plots/burnin_cg.eps}
\caption{\label{fig:burnin} The $\chi^2$ of each step of the full MCMC
  for one case.}
\end{figure}

@@

\item[5) {\bf DD}:] red dashed curve.  When the correct model is
  fitted to a disc-source, the best fit $\chi^2=0.91$ is good and
  $R_p$ is recovered within the uncertainty estimate.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{figures/data_cc.eps}
\includegraphics[width=0.9\hsize]{figures/data_dd.eps}
\includegraphics[width=0.9\hsize]{figures/data_gg.eps}
\caption{\label{fig:mockdata} Three different mock datasets with
  three different parametrizations fitted to each --- crescent (red),
  uniform-disk (blue) and Gaussian disk (green).}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{figures/Rp4all.eps}
\caption{\label{fig:mcmc} Posterior probability distribution for the
  source size $R_p$.  The vertical line is the correct value. Same
  color represents the same dataset whereas same line style
  corresponds to same model fit.  The legend gives the reduced
  $\chi^2$ of the best fit in each case.}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{figures/Rhalf_RnRp.eps}
  \includegraphics[width=0.9\hsize]{figures/aRp_bRp.eps}
\caption{\label{fig:crescentfit} The 2$\sigma$ contours (or error ellipses)
  of the crescent model when fitting with the three different
  datasets.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{figures/burnin_cg.eps}
\caption{\label{fig:burnin} The $\chi^2$ of each step of the full MCMC
  for one case.}
\end{figure}

@@

\item[5) {\bf DD}:] blue dashed curve.  When the correct model is
  fitted to a disc-source, the best fit $\chi^2=0.91$ is good and
  $R_p$ is recovered within the uncertainty estimate.

### 2016-03-09 paper1/theory.tex
reprocessed eps files

\begin{figure}
\centering
\includegraphics[width=0.9\hsize,bb=0 0 576 432
		]{plots/IRIS567_path_2.eps}
\caption{\label{fig:magnification_map} Magnification map used in the second part of the presented work. The white line marks the trajectory of the center of the sources for which the lightcurves presented in figure 12 are generated.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .49\textwidth]{plots/infinite_fold_ar.eps}
\caption{\label{fig:infinite_fold} Source profiles for Gaussian, disk,
  crescents (right) and magnification map for an infinite fold
  (left). Objects have the same $S_{0}$ and $r_{1/2}$. The black arrow marks the direction of motion of the
sources relative to the caustic.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .49\textwidth]{plots/figure_rhalf.eps}
\caption{\label{fig:geom_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth ,bb=0 0 576 520
	]{plots/S1D_all.eps}
	\includegraphics[width = 0.48\textwidth ,bb=0 0 576 520
	]{plots/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, Gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/S1D_var_a.eps}
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/4avar_magnification.eps}
\caption{\label{fig:lightcurve_disk} Lightcurves of crescent sources with $R_n$ = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/S1D_var_rn_a_poz.eps}
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/5Rn_back_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/S1D_var_rn_a_neg.eps}
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/5Rn_forw_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/ch_points.eps}
        \includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/ch_instances.eps}
\caption{\label{fig:char_points} The characteristic points and instances of a crescent source's one dimensional profile and microlensing lightcurve. }
\end{figure}

@@

\begin{figure}
\centering
        \includegraphics[width = 0.48\textwidth]{plots/M87_image.eps}
\caption{\label{fig:M87_image} The simulated image of M87's black hole sillouette obtained by \citep{2012MNRAS.421.1517D} from a GRMHD simulation presented in \citep{2009MNRAS.394L.126M}. The color bar is linear and scaled to reach value 1 for the maximum brightness. Points p2 and p3, mark the start and end of the equivalent dark disk and are associated to the moment of their overlap with the caustic t2 and t3.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth,bb=0 0 576 520
	]{plots/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained from the numerical integration along the ordonata axis of the source image (figure 9) is presented in the left subplot. The corresponding lightcurve associated to the 1D profile is presented in the right subplot. The points p2 and p3 mark the start and end of the equivalent dark disk and are associated to the moments of their overlap with the caustic: t2 and t3.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{figures/IRIS567_path.eps}
\caption{\label{fig:magnification_map} Magnification map used in the second part of the presented work. The white line marks the trajectory of the center of the sources for which the lightcurves presented in figure 12 are generated.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .49\textwidth]{figures/infinite_fold_ar.eps}
\caption{\label{fig:infinite_fold} Source profiles for Gaussian, disk,
  crescents (right) and magnification map for an infinite fold
  (left). Objects have the same $S_{0}$ and $r_{1/2}$. The black arrow marks the direction of motion of the
sources relative to the caustic.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .49\textwidth]{figures/figure_rhalf.eps}
\caption{\label{fig:geom_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/S1D_all.eps}
	\includegraphics[width = 0.48\textwidth]{figures/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, Gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/S1D_var_a.eps}
	\includegraphics[width = 0.48\textwidth]{figures/4avar_magnification.eps}
\caption{\label{fig:lightcurve_disk} Lightcurves of crescent sources with $R_n$ = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_poz.eps}
	\includegraphics[width = 0.48\textwidth]{figures/5Rn_back_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/S1D_var_rn_a_neg.eps}
	\includegraphics[width = 0.48\textwidth]{figures/5Rn_forw_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/ch_points.eps}
        \includegraphics[width = 0.48\textwidth]{figures/ch_instances.eps}
\caption{\label{fig:char_points} The characteristic points and instances of a crescent source's one dimensional profile and microlensing lightcurve. }
\end{figure}

@@

\begin{figure}
\centering
        \includegraphics[width = 0.48\textwidth]{figures/M87_image.eps}
\caption{\label{fig:M87_image} The simulated image of M87's black hole sillouette obtained by \citep{2012MNRAS.421.1517D} from a GRMHD simulation presented in \citep{2009MNRAS.394L.126M}. The color bar is linear and scaled to reach value 1 for the maximum brightness. Points p2 and p3, mark the start and end of the equivalent dark disk and are associated to the moment of their overlap with the caustic t2 and t3.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{figures/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth]{figures/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained from the numerical integration along the ordonata axis of the source image (figure 9) is presented in the left subplot. The corresponding lightcurve associated to the 1D profile is presented in the right subplot. The points p2 and p3 mark the start and end of the equivalent dark disk and are associated to the moments of their overlap with the caustic: t2 and t3.}
\end{figure}
